\documentclass[../main.tex]{subfiles}


\begin{document}
\raggedright

Blockchains production base is transparency. It will allow the storage of forms and data to be secure and encrypted with no central database holding everything. However, Blockchain is more useful when a digital property is involved as it works efficiently with trading and not storage for single entries. It still is a new technology, and there is not enough detail on how exactly it can be helpful.\cite{vergeblockchain}. Being a new advancement, it might not be stable enough in the long run and education on a Blockchain based system would be required for further maintenance and bug fixing. \\[2mm]

Smart Phone Applications, on the other hand, are used almost daily. There are officially more Mobile Phones than people in the world\cite{morephones}. All students use smartphones, and it would be easy for them to use a simple application to fill in all the questions and feedback for the form. However, the same brings an issue for data processing and readability for the scrutiny committee and student report. The scrutiny committee would want the data to be readily available, not having to download a new application where they can barely read the large amounts of data and attachments uploaded by the student. Using mobile applications would allow instant communication as the system can use notifications for constant feedback and review processes but would only be advantageous for the students as they will be able to fill the forms on their fingertips, on the other end the scrutiny committee and other stakeholders will not like the idea of having to do everything from a small five inch phone. \\[2mm]

Web-Based Systems have been in the market for quite a while now, and they still are the most used compared to any other digital technology\cite{morewebsites}.
Being accessible from any internet connected device this makes it usable from Mobile Phones, Desktops/Personal Computers and other devices. Web system would also allow the scrutiny committee to access the system on a larger screen and allow them to make any significant changes and requests with enough detail and also move data from one stakeholder to another quickly such as exporting as a PDF document. Students already use MUSE\cite{muse} and so our system would only need to be linked to the University of Sheffield logins allowing all users to log in smoothly. 
\end{document}
