\documentclass[../main.tex]{subfiles}

\begin{document}
\raggedright
Different types of complications showed up while compiling the code. The most difficult ones are described below under two sections; Students and Secretary. The Scrutiny Panel did not have as many severe complications as most of the code was reused from the other two. 

\subsection{Student Panel}

\subsubsection{Dashboard}
Issue: Calculate based on forms and not each module within the form. \\
Solution: Use nested FOR loops to calculate statistics for each module within the form and only display the final count as the main form statistic.                                                                  \\[2mm]


\subsubsection{New Form}
Issue: Create module input fields based on the GET parameter value and allow each of the modules to be stored into the database. \\
Solution: Retrieve the GET parameter value from views.py and import it into forms.py where the input fields are generated from. Use a FOR loop to create an input field with increasing HTML attributes example, unitcode1 \\[2mm]

Issue: Allow only ZIP files to be added and validated.                                                                 \\
Solution: Create a Django validations.py function which detects the format of the file and rejects if it is not a ZIP.                                                                                               \\[2mm]

Issue: Store files with the same name without replacing them.                                                                   \\
Solution: Rename the uploaded file by adding a five digit random string to the end to prevent files being replaced when stored.                                                                                          \\[2mm]

\subsubsection{View Form}
Issue: Prevent other users from accessing current users form.                                                                   \\
Solution: Create validations which check if the form belongs to the currently logged user, if so, then the user is allowed to access it.                                                                               \\[2mm]


\subsection{Secretary Panel}

\subsubsection{Dashboard}
Issue: Calculate based on forms and not each module within the form.\\
Solution: Use nested FOR loops to calculate statistics for each module within the form and only display the final count as the main form statistic.                                                     \\[2mm]

\subsubsection{View Form}
Issue: Modal popup to edit form details would load on a different page instead of current one.\\
Solution: Instead of having the modal on a different file, having it in the current file with a JavaScript code to retrieve data and fill it in allowed the popup to load on the current page seamlessly.\\[2mm]

Issue: Multiple POST forms would bring about issues when working on views.py as the controller.\\
Solution: Provide each POST request with a unique 'name' attribute to differentiate which part of the views.py it should access using IF statements.\\[2mm]

Issue: Switch-case Toggle HTML would not change the switch based on the current value in the database.\\
Solution: Added a JavaScript code to manually get the value from the database and switch the toggle CSS.                                                                                                \\[2mm]


\end{document}
