\documentclass[../main.tex]{subfiles}


\begin{document}
\raggedright

Blockchain is built on transparency. It will allow the storage of forms and data to be secure and encrypted with no central database holding everything. However, Blockchain is more useful when a digital property is involved as it works efficiently with trading and not storage for single entries. It still is a new technology and there is not enough detail on how exactly it can be helpful\cite{vergeblockchain}.\\[2mm]

Smart Phone Applications on the other hand are used almost daily. There are officially more Mobile Phones than people in the world\cite{morephones}. Students all use smart phones and it would be easy for them to use a simple application to fill in all the questions and feedbacks for the form. However, the same brings an issue for data processing and readability for the examination board and student report. The scrutiny committee would want the data to be readily available, not having to download a new application where they can barely read the large amounts of data and attachments uploaded by the student. Using mobile applications would allow instant communication as the system can use notifications for constant feedback and review processes. \\[2mm]

Web Based Systems have been in the market for quite a while now and they still are the most used compared to any other digital technology\cite{morewebsites}.
Being accessible from any internet connected device this makes it usable from Mobile Phones, Desktops/Personal Computers and other devices. Web system would also allow the scrutiny committee to access the system and view it on a big screen. 
\end{document}
